Controlling the rheological properties of well-defined polyelectrolytes hydrogels by fine tuning their ion pairing process

### 2015-12-20 ion_pairing_paper.tex
include synthesis.pdf, generated from synthesis.pgf
Metathesis

The phosphonate terminated polymer \ce{PBr}, which is the common basis to all studied polymer was synthesized according to our previously reported methodology; allowing us to obtain a well-controlled linear polymer ($Mw= \SI{5614}{\dalton}$, $Mw/Mn = 1.08$; S2, S3, Figure S1) .9, 10 All subsequent transformations of the polymer structures were achieved using the same initial batch of material. Nucleophilic addition of N-Methylimidazole or N-methylpyrrolidine to a heated solution of \ce{PBr} in THF afforded the corresponding poly(imidazloium) and poly(pyrrolidinium) compounds. In these cases, as an inherent consequence of the structure of the starting material, charge neutrality is provided by bromide counter ions, and the polymer will be referred to as \ce{PIm+Br-} and \ce{PPyr+Br-}, respectively (Scheme~\ref{sch:synthesis}).

\begin{scheme}
\caption{Synthesis of \ce{PIm+Br-} and \ce{Ppyr+Br-} and their intermediate. $n=70$}
\label{sch:synthesis}
\end{scheme}

@@

\begin{scheme}
\caption{Anionic metathesis reaction.}
\label{sch:metathesis}
\end{scheme}

>>>>

The phosphonate terminated polymer \ce{PBr}, which is the common basis to all studied polymer was synthesized according to our previously reported methodology; allowing us to obtain a well-controlled linear polymer ($Mw= \SI{5614}{\dalton}$, $Mw/Mn = 1.08$; S2, S3, Figure S1) .9, 10 All subsequent transformations of the polymer structures were achieved using the same initial batch of material. Nucleophilic addition of N-Methylimidazole or N-methylpyrrolidine to a heated solution of \ce{PBr} in THF afforded the corresponding poly(imidazolium) and poly(pyrrolidinium) compounds. In these cases, as an inherent consequence of the structure of the starting material, charge neutrality is provided by bromide counter ions, and the polymer will be referred to as \ce{PIm+Br-} and \ce{PPyr+Br-}, respectively (Scheme~\ref{sch:synthesis}).

\begin{scheme}
\includegraphics{synthesis.pdf}
\caption{Synthesis of \ce{PIm+Br-} and \ce{Ppyr+Br-} and their intermediate. $n=70$}
\label{sch:synthesis}
\end{scheme}

@@

\begin{scheme}
\includegraphics{metathesis.pdf}
\caption{Anionic metathesis reaction. As above, \ce{Nu+} corresponds either to pyrrolidinium or imidazolium.}
\label{sch:metathesis}
\end{scheme}
